Automated detections reveal the social information in the changing infant view

### 2020-08-24 writeup-paper/draft_apa_blinded.Rmd
latest paper draft

abstract: |
  Social information plays a key role in infants\' early linguistic and cognitive development. Yet infants locomotor abilities also develop continuously as they learn to sit, crawl, stand, and walk. How do these postural developments affect infants access to the social information relevant for early learning? To address this question, we first created a rich annotated dataset of naturalistic play sessions between infants and their caregivers with sets of novel and familiar toys (N=36, 8-16 months of age), recording both egocentric and third-person video. We then developed an automated analysis method using a pose detection model (Zhang et al., 2017) to detect the faces and hands in the infant view, allowing us to analyze the entirety of this dataset. We found that infants\' posture and orientation to their caregiver changed dramatically across this age range and modulated infants access to social information; infants who were sitting or standing with their caregiver at a close distance tended to have the most faces and hands in their visual field. We also applied our automated method to a second egocentric video dataset where one-year-olds explored a large play room with their caregivers  (Franchak et al., 2017), replicating and extending their findings. Together, these results establish the validity of a new method for detecting social information and confirm that motoric developments play a significant role in shaping the social information that infants have access to. We propose that the combined use of head-mounted cameras and the application of new computer vision techniques is a promising avenue for re-utilizing rich video datasets and understanding how the statistics of infants\' visual and linguistic experience change over development.

keywords          : "Postural developments, headcam, social information, face detection, pose detection"
wordcount         : "XXX"

@@

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=FALSE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(ggthemes)
library(lme4)
library(gridExtra)
library(assertthat)
library(tidyverse)
library(viridis)
library(papaja)
library(png)
library(magick)
library(lmerTest)
```

@@

From their earliest months, infants are deeply engaged in learning from others. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development; @bruner1975]. And as infants reach their first birthday, they also tend to follow [@yu2013joint; @yu2017hand] and imitate the gestures of their caregivers (e.g., pointing).

Infants ability to process these social cues may provide strong scaffolding for early word learning. Longitudinal studies provide some evidence for this link: children’s level of joint engagement with their mother at 9-12 months predicts both their receptive and productive vocabularies [@carpenter1998] and 10 month-olds who follow an adult’s gaze (in an experimental context) have larger vocabularies at 18 months and throughout the second year of life [@brooks2005; @brooks2008]. While the relationship between hand-following and language development has been less well characterized, infants who follow their caregivers’ hands tend to be those who spend more time jointly attending to events with their caregivers [@yu2017hand].

Relatively little work, however, has quantified how often infants see and use these kinds of social cues in naturalistic learing environments. By using head-mounted cameras to record what infants see, researchers have begun to document the infant egocentric perspective [@yoshida2008] and to quantify the information -- social and otherwise -- available to infants as they learn. While head-mounted camera data do not provide explicit information on where infants are attending, some work suggests that infants orient their head towards what they are focusing on -- putting those people or objects in view [@yoshida2008]. Initial recordings using this technique during in-lab play sessions revealed a different view than many imagined: instead of being dominated by faces, the infant perspective contained close up views of primarily toys and hands [@yoshida2008; @franchak2011; @yu2017hand]. Subsequent research has revealed that the infant view is far from a unitary construct, undergoing dramatic changes as infants grow. Recordings from home environments suggest that the viewpoints of very young infants -- less than 4 months of age -- do indeed contain persistent and frequent views of faces [@fausey2016; @jayaraman2017faces] but that the infant view tends to contain more and more hands as infants grow older.

These changes in perspective are likely the downstream consequence of a myriad factors, chief of which may be infants' evolving locomotive abilities: an infant's ability to sit, crawl, stand, or walk structures the way they interact with the things and people in their world. Infants' locomotive abilities can change rapidly: the physical body of an infant can lengthen up to 2cm in 24 hours [@lampl1993evidence], leading to changes in their physical abilities from one day to the next. These motoric developments can be thought of as gateways that open up entirely new phases of development [@iverson2010], and cause a cascade of changes in infants ability to interact with their world and the people in it [@karasik2014].

Thus, infants’ changing locomotor abilities may shape the social cues that infants' see and seek out, in turn impacting their cognitive and linguistic abilities. Supporting this idea, infants experience with sitting predicts their success at 3D object completion tasks [@soska2010systems] as well as their receptive vocabulary [@libertus2016sit]. And as children begin crawling [@adolph1998roles] -- or scooting or cruising [@patrick2012developmental] -- they are no longer constrained to the same spot that their caregivers last placed them in. Yet while crawlers can choose where to go and what they see to a much greater degree, they also appear to spend much of their time in a world populated by floors and knees; during spontaneous play, toddlers are more likely to look at the floor while crawling than while walking [@franchak2011], when they have full visual access to their environment and the people in it [@kretch2014].

On one view, it is children’s ability to stand and walk that fundamentally changes their ability to access social information (e.g., facial expressions, gaze cues, pointing) relative to children who are still crawling and sitting [@walle2016infant]. In turn, this ability to access more detailed social information could allow infants to learn words quicker and more efficiently, facilitating language growth [@walle2016infant]. Supporting this idea, walking infants make different kinds of object-related bids for attention from their caregivers than crawling infants, and tend to hear more action directed statements (e.g., “open it”) [@karasik2014]; further, in an observational study, @walle2014 also found that children who were able to walk had both higher receptive and productive vocabularies. However, not all evidence supports this view: some parental report data suggest a weak relationship between walking and the onset of language [@moore2019point], and head-mounted eye-tracking data have highlighted the role of infants’ in-the-moment posture -- and that of their caregivers’ -- in what infants’ see, finding that these factors are better predictors of the social information in view than their locomotor status per se (i.e., “walker” vs “crawler”) [@franchak2017see].

Understanding this nuanced relationship between the social information in the infant view and their motoric and linguistic development has remained challenging. Indeed, different kinds of play sessions (e.g., exploring novel environments vs. playing with novel objects) might modulate the degree to which infants’ posture changes the social information in view. Furthermore, no work to date has directly examined how the availability of social information changes in naturalistic language learning contexts. For example, it is unclear if and how the social information in view changes during the naming events for different objects (e.g, “Look, a [ball]”).

More broadly, the field is in need of computational tools to reutilize rich video datasets and to understand the generalizability of findings across different populations, tasks, and age-ranges. While the field has assembled many head-mounted camera datasets, conducting new analyses on these videos has remained prohibitively time-consuming due to a lack of computational tools for annotations. Instead, hundreds of hours of manual annotations have been required to analyze a fraction of the available frames for a given analysis. Thus, despite containing a wealth of information about the structure of parent-child interactions, these datasets have thus gone dramatically underused.

Recent innovations in computer vision hold promise for automated annotations of the infant view. Over the past decade, deep neural networks have become dramatically better at a wide range of visual tasks, including object classification, @simonyan2014very], scene categorization [@zhou2017places], and pose detection [@zhang2016], arguably facilitating our understanding of visual perception [@peterson2018evaluating, @vanrullen2017perception] and improving computational neuroscience [@kietzmann2018deep]. However, as most models have been trained on photographs or videos taken from the adult perspective, it is still unclear how easily these models can be applied to videos taken from the infant perspective.

In this paper, we thus first validate a model for the automated detection of faces and hands in the infant view, using a open-source model of pose detection -- OpenPose[@zhang2016; @cao2017realtime] -- that provides pose, face, and hand keypoints for every person in an image. We compare the detection accuracy of OpenPose with that of both older and more specialized models of face detection and demonstrate the usability of this off-the-shelf model for quantifying the faces and hands in the infant view.

We then apply this automated method to a head-mounted camera dataset collected in our lab to directly examine the role of postural developments on the social information in the infant view during language learning. Specifically, we constructed a dataset where infants and caregivers played freely using a set of novel and familiar objects; 8, 12, and 16 months-olds (N=36; N=12 in each age group) participated to ensure a wide range of locomotor abilities. Infants’ in-the-moment posture and orientation relative to their caregiver were hand annotated and all play sessions were transcribed. This cross-sectional design thus allowed us to directly examine the relative contributions of age vs. postural developments on children’s visual access to social information, and how the avaliability of social cues changes relative to naming events (e.g., “Yes, you like the [ball!]”).  Broadly, we predicted that there would be differential access to social information based on children's postural developments: crawling infants would see fewer faces/hands because they would primarily be looking at the ground, while walking toddlers would have access to a richer visual landscape with greater access to the social information in their environment.

To examine the robustness of our automated method and the generalizability of our findings, we applied OpenPose [@cao2017realtime] to the dataset collected in @franchak2017see, where one-year-olds wore head-mounted eye-tracking cameras during a play session and their in-the-moment posture was hand-annotated. Unlike the present dataset, infants and caregivers roamed a large, open playroom and explored different toys placed throughout. We thus analyzed this dataset with the goal of both (1) validating our automated method on a very different kind of dataset, attempting to replicate their primary findings originally obtained with a head-mounted eye-tracker  (2) examining whether the proportion of hands in view also varies with infants’ posture in an exploratory play session.

# Methods
## Free-play video dataset  
A primary goal of this project was to provide a annotated, open dataset for other researchers to examine the effects of postural developments and labeling behavior during naturalistic parent-child interactions. We thus invited caregivers of 8, 12, and 16-month-olds to participate in play sessions where they were provided with pairs of novel and familiar objects (e.g., a ball and a microfiber duster, called a "zem") in a small playroom in a lab (approximately 10' x 10'). Infants wore head-mounted cameras equipped with a fish-eye lens (see Head-mounted camera), a tripod-mounted camera captured a third-person view of the play session. Using these video data, infants' posture and orientation to their caregiver were hand-coded and annotated for the entirety of the play session. All videos were transcribed, and MacArthur CDIs were collected for all children who particpated. All materials have been made publicly avaliable on Databrary for whom the parents provided sharing consent (29/36 dyads) via https://nyu.databrary.org/volume/101

@@

all_subs %>%
  left_join(inc_subs) %>%
  filter(inc==TRUE) %>%
  group_by(age_group) %>%
  summarise(n = sum(inc),
            percent_included = mean(inc),
            age = mean(age.at.test, na.rm=TRUE),
            video_length = mean(len.min, na.rm=TRUE),
            female = sum(gender=="female", na.rm=TRUE)) 
  # xtable %>%
  # print(digits = 2, include.rownames=FALSE,table.placement = "H", type="latex", comment = F)

# <!-- \caption{\label{tab:pop} Demographics by age group.} -->
```
Our final sample consisted of 36 infants and children, with 12 participants in three age groups: 8 months (6 F), 12 months (7 F), and 16 months (6 F). Participants were recruited from the surrounding community via state birth records, had no documented disabilities, and were reported to hear at least 80 percent English at home. Demographics and exclusion rates are given in the table below (see Table 1).

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
\hline
Group & N & \% incl. & Avg age & Avg video length (min) \\
\hline
8 mo. &   12 & 0.46 & 8.71 & 14.41 \\
12 mo. &  12 & 0.40 & 12.62 & 12.71 \\
16 mo. &  12 & 0.31 & 16.29 & 15.10\\
\hline
\end{tabular}
\caption{Exclusion rates and summary demographics for the infants included in the study.} 
\end{table}

@@

We used a head-mounted camera ("headcam") that was constructed from a small camera attached to a soft elastic headband.[^2]  Initial participants wore an MD-80 camera, which was then replaced by a Veho pro camera which had better battery life and a larger view angle. The view angle of the MD-80 camera was $32^{\circ}$ horizontal by $24^{\circ}$ vertical, and we attached a fish-eye lens to the camera to increase the view angle to $64^{\circ}$ horizontal by $46^{\circ}$ vertical. The view angle of the Veho pro camera was wider, $47^{\circ}$ horizontal by $36^{\circ}$ vertical. Videos captured by MD-80/Veho cameras  were 640x480/720x480 pixels, respectively, and both cameras had a frame rate of ~30 frames per second. To ensure taht detections across these different cameras were comparable, we excluded detections from the outer edges of the videos taken with the MD-80 cameras based on these view angle differences in our main analyses (i.e. excluding top/bottom 13% of the frames, and left/right 10% of the frames).

[^2]: Detailed instructions for creating this headcam can be found  at \url{http://babieslearninglanguage.blogspot.com/2013/10/how-to-make-babycam.html}.

However, the vertical field of view of the cameras were still considerably reduced compared to the infants' field of view, which spans around 100--120$^{\circ}$ in the vertical dimension by 6-7 months of age [@mayer1988;@cummings1988]. As we were primarily interested in the presence of faces in the child's field of view, we chose to orient the camera upwards to capture the entirety of the child's upper visual field where the child is likely to see adult faces, understanding that this decision limited our ability to detect hands (especially those of the child, which are typically found at the bottom of the visual field).

@@

## OpenPose detections key
## faceOP, wristOP == faces and wrists in equalized FOV across cameras
## faceOPAll, wristOPAll == faces and wrists of all confidences across all areas of the frames
## "faceOPStrict", "wristOPStrict" == faces and wrists in equalized FOV across cameras with high confidence
## "faceOPStrictAll", "wristOPStrictAll" == faces and wrists across all areas of the frames  with high confidence

## make long form version for plotting both face detections on same graph
dlong <- d %>%
  mutate(id = paste(subid,frame)) %>%
  gather(key = detectorType, value = detection, faceMT, faceOP, faceOPAll, faceOPStrict, faceOPStrictAll, faceVJ, wristOP, wristOPAll, wristOPStrict, wristOPStrictAll) %>%
  mutate(detectorType=as.factor(detectorType))  %>%
  mutate(detection = replace_na(detection,FALSE)) ## few frames where OP didn't have detections

@@

#### Posture and caregiver orientation annotations
We created custom annotations to describe the child's physical posture (i.e. standing) and the orientation of the caregiver relative to the child (e.g. far away). The child's posture was categorized as being carried, prone (crawling or lying), sitting, or standing. The caregiver's orientation was characterized as being close, far, or behind the child (independent of distance). For the first two annotations (close/far from the child), the caregiver could either be to the front or side of the child. All annotations were made by a trained coder using the OpenSHAPA/Datavyu software [@adolph2012toward]. Times when the child was out of view of the tripod camera were marked as uncodable and were excluded from these annotations; similarily, times when the child was being carried or the caregivers were out of the frame were marked as uncodable for caregiver orientation. On average, posture or orientation was uncodable from 1-2 minutes of data in each child (seconds excluded from analysis for posture, M = `r round(NA_rates$mean_na_posture,2)`s, SD = `r round(NA_rates$sd_na_posture,2)`s; orientation; M = `r round(NA_rates$mean_na_posture,2)`s, SD = `r round(NA_rates$sd_na_posture,2)`s), and these rates did not vary substantially with the age of the child.  To assess the reliability of these annotations, a second coder annotated videos from three different children to calculate Cohen's kappa (posture, irr = .82; caregiver orientation, irr = .73).

@@

## Face and hand detection
We evaluated three detection systems for the ability to measure infants' visual access to faces. The first of these is the most commonly-used and widely available face detection algorithm: Viola-Jones  [@viola2004robust]. We used this algorithm as a benchmark for performance, as while it can achieve impressive accuracy in some situations, it is notoriously bad at dealing with occluded faces [@scheirer2014perceptual]. We next tested the performance of two face detectors that both made use of relatively recently developed Convolutional Neural Networks (CNNs) to extract face information. The first algorithm was specifically optimized for face detection, and the second algorithm was optimized to extract pose information of all the individuals in an image, operationalized as information about the position of 18 different body parts.  For this second algorithm [OpenPose; @cao2017realtime], we used the agent's nose (one of the body keypoints detected) to operationalize the presence of faces, as any half of a face necessarily contains a nose.

@@

### Algorithms
Viola Jones, the first face detection system, made use of a series of Haar feature-based cascade classifiers [@viola2004robust] applied to each individual frame. The second algorithm (based on work by @zhang2016) uses multi-task cascaded convolutional neural networks (MTCNNs) for joint face detection and alignment, built to perform well in real-world environments where varying illuminations and occlusions are present. We used a Tensorflow implementation of this algorithm available at https://github.com/davidsandberg/facenet.

@@

# Results
First, we report the accuracy of the automated detectors, as assessed by comparison to hand-labelled frames from the free-play video dataset described above. We then apply one of these automated detectors (OpenPose) to the entirety of this video dataset, and use these outputs to examine how postural developments influence children's visual access to faces and hands from 8-16 months of age, as well as how access to these social cues changes during labeling events (e.g., do you see the [zem]?). Finally, we apply this same automated detector to another video dataset [@franchak2017see], replicating and extending their findings on the effects of posture on visual access to social information.

```{r exampledetections, fig.env = "figure", out.width="100%", fig.pos = "H", fig.label="exampledetections", fig.cap = "Example detections made by OpenPose from children in each age group."}

knitr::include_graphics("images/exampe_detections.png")

@@

## Only keep what we're analyzing
dlong <- dlong %>%
  filter(detectorType %in% c('OpenPose-Faces','OpenPose-Wrists'))

@@

```{r failures, fig.env = "figure", out.width="50%", fig.pos = "H", fig.label="headcam", fig.cap = "Example failed detections from OpenPose, showing both false positives and false negatives (i.e. missed detections)."}
knitr::include_graphics("images/example_failures.png")
```

@@

\begin{table}[ht]
\centering
\begin{tabular}{llrrr}
  \hline
Algorithm & Sample\ Type & P & R & F \\ 
  \hline
MTCNN-Faces & High density & 0.89 & 0.92 & 0.90 \\ 
  MTCNN-Faces & Random & 0.94 & 0.62 & 0.75 \\ 
  OpenPose-Faces & High density & 0.78 & 0.93 & 0.84 \\ 
  OpenPose-Faces & Random & 0.72 & 0.80 & 0.76 \\ 
  OpenPose-Faces-Strict & High density & 0.97 & 0.65 & 0.78 \\ 
  OpenPose-Faces-Strict & Random & 0.97 & 0.62 & 0.76 \\ 
  ViolaJones-Faces & High density & 0.96 & 0.44 & 0.60 \\ 
  ViolaJones-Faces & Random & 0.44 & 0.38 & 0.41 \\ 
  \hline
  \hline
  OpenPose-Wrists & High density & 0.66 & 0.96 & 0.78 \\ 
  OpenPose-Wrists & Random & 0.88 & 0.29 & 0.43 \\ 
  OpenPose-Wrists-Strict & High density & 0.95 & 0.44 & 0.60 \\ 
  OpenPose-Wrists-Strict & Random & 1.00 & 0.10 & 0.18 \\
   \hline
\end{tabular}
\caption{Detector performance on both high density samples (where proportion of targets detected was high) and random samples (where frames were randomly selected). P, R, and F denote precision, recall, and F-score, respectively. "Strict" denotes when we only considered high confidence detections.} 
\vspace{-1em}
\end{table}

## Study 1: Access to social information during postural developments

>>>>

abstract: |
•	We provided an open, annotated dataset of naturalistic parent-child interactions during a play session with novel and familiar toys, recording egocentric and third-person views.
•	We develop a novel method using a pose detection model to automatically quantify the faces and hands in the infant view.
•	We apply our novel method to this and another egoecentric video dataset, confirming that locomotive developments shape the faces and hands that infants see.
•	The combined use of head-mounted cameras and automated analyses have the potential to reveal the changing statistics of the infant view.

  Social information plays a key role in infants\' early linguistic and cognitive development. Yet infants locomotor abilities also develop continuously as they learn to sit, crawl, stand, and walk. How do these postural developments affect infants access to the social information relevant for early learning? To address this question, we first created a rich annotated dataset of naturalistic play sessions between infants and their caregivers with sets of novel and familiar toys (N=36, 8-16 month-olds), recording both egocentric and third-person video. We then developed an automated analysis method using a pose detection model to detect the faces and hands in the infant view. We found that infants\' posture and orientation to their caregiver changed dramatically across this age range and modulated infants access to social information; infants who were sitting or standing with their caregiver at a close distance tended to have the most faces and hands in their visual field. We applied this automated method to a second egocentric video dataset from a previous study, replicating and extending their findings on the influence of infants' posture on the social information in view. Together, these results establish the validity of a new method for detecting social information in egocentric videos and confirm that motoric developments play a significant role in shaping the social information that infants have access to. The combined use of head-mounted cameras and new computer vision techniques is a promising avenue for understanding how the statistics of infants\' visual and linguistic experience change over development.

keywords          : "Postural developments, headcam, social information, face detection, pose detection"
wordcount         : "7324"

@@

figsintext        : yes
figurelist        : yes
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_docx
---

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=FALSE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(ggthemes)
library(lme4)
library(gridExtra)
library(assertthat)
library(tidyverse)
library(viridis)
library(papaja)
library(png)
library(magick)
library(lmerTest)
```

@@

From their earliest months, infants are deeply engaged in learning from others. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development; @bruner1975]. And as infants reach their first birthday, they also tend to follow [@yu2013joint; @yu2017hand] and imitate the gestures of their caregivers (e.g., pointing). Infants ability to process these social cues may provide strong scaffolding for early word learning. Longitudinal studies provide some evidence for this link: children’s level of joint engagement with their mother at 9-12 months predicts both their receptive and productive vocabularies [@carpenter1998] and 10 month-olds who follow an adult’s gaze (in an experimental context) have larger vocabularies at 18 months and throughout the second year of life [@brooks2005; @brooks2008]. While the relationship between hand-following and language development has been less well characterized, infants who follow their caregivers’ hands tend to be those who spend more time jointly attending to events with their caregivers [@yu2017hand].

Relatively little work, however, has quantified how often infants see and use these kinds of social cues in naturalistic learning environments. By using head-mounted cameras to record what infants see, researchers have begun to document the infant egocentric perspective [@yoshida2008] and to quantify the information -- social and otherwise -- available to infants as they learn. While head-mounted camera data do not provide explicit information on where infants are attending, some work suggests that infants orient their head towards what they are focusing on -- putting those people or objects in view [@yoshida2008]. Initial recordings using this technique during in-lab play sessions revealed a different view than many imagined: instead of being dominated by faces, the infant perspective contained close up views of primarily toys and hands [@yoshida2008; @franchak2011; @yu2017hand]. Subsequent research has revealed that the infant view undergoes dramatic changes as infants grow. Recordings from home environments suggest that the viewpoints of very young infants -- less than 4 months of age -- do indeed contain persistent and frequent views of faces [@fausey2016; @jayaraman2017faces] but that the infant view tends to contain more and more hands as infants grow older.

These changes in perspective are likely the downstream consequence of myriad factors, chief of which may be infants' evolving locomotive abilities: an infant's ability to sit, crawl, stand, or walk structures the way they interact with the things and people in their world. Infants' locomotive abilities can change rapidly: the physical body of an infant can lengthen up to 2cm in 24 hours [@lampl1993evidence], leading to changes in their abilities from one day to the next. These motoric developments can be thought of as gateways that open up entirely new phases of development [@iverson2010], causing a cascade of changes in an infant's ability to interact with their world and the people in it [@karasik2014]. Thus, infants’ changing locomotor abilities may shape the social cues that infants' see and seek out, in turn impacting their cognitive and linguistic abilities.

However, understanding the nuanced relationship between the social information in the infant view and their motoric and linguistic development has remained challenging. For example, as children begin crawling [@adolph1998roles] -- or scooting or cruising [@patrick2012developmental] -- they are no longer constrained to the same spot that their caregivers last placed them in. Yet while crawlers can choose where to go and what they see to a much greater degree, they also appear to spend much of their time in a world populated by floors and knees; during spontaneous play, toddlers are more likely to look at the floor while crawling than while walking [@franchak2011], when they have full visual access to their environment and the people in it [@kretch2014].
Further, infants' experience with sitting predicts their success at 3D object completion tasks [@soska2010systems] as well as their receptive vocabulary [@libertus2016sit], suggesting the importance of focused play sessions for language development.

Others have posited that it is children’s ability to stand and walk that fundamentally changes their ability to access social information (e.g., facial expressions, gaze cues, pointing) relative to children who are still crawling and sitting [@walle2016infant], which in turn allow infants to learn words quicker and more efficiently [@walle2016infant]. Supporting this idea, walking vs. crawling infants tend to make different kinds of object-related bids for attention from their caregivers [@karasik2014], hear more action directed statements (e.g., “open it”) [@karasik2014], and have higher receptive and productive vocabularies [@walle2014]. However, not all evidence supports this view: parental report data suggest a weak relationship between walking and the onset of language [@moore2019point], and head-mounted eye-tracking data from one-year-olds highlights the role of infants’ in-the-moment posture -- and that of their caregivers’ -- in what infants’ see, finding that these factors are better predictors of the social information in view than their locomotor status per se (i.e., “walker” vs “crawler”) [@franchak2017see].

Broadly, the field is in need of computational tools to reuse these rich video datasets and understand the generalizability of findings across different populations, tasks, and age-ranges. For example, different kinds of play sessions (e.g., exploring novel environments vs. playing with novel objects) might modulate the degree to which infants’ posture changes the social information in view. Yet while the field has assembled many head-mounted camera datasets, conducting new analyses on these videos has remained prohibitively time-consuming due to a lack of computational tools for annotations. Instead, hundreds of hours of manual annotations have been required to analyze a fraction of the available frames for a given analysis. Thus despite containing a wealth of information about the structure of parent-child interactions, these datasets have thus gone dramatically underused.

Recent innovations in computer vision hold promise for automated annotations of the infant view. Over the past decade, deep neural networks have become dramatically better at a wide range of visual tasks, including object classification [@simonyan2014very] scene categorization [@zhou2017places], and pose detection [@zhang2016], arguably facilitating our understanding of visual perception [@peterson2018evaluating; @vanrullen2017perception] and improving computational neuroscience [@kietzmann2018deep]. However, as most models have been trained on photographs or videos taken from the adult perspective, it is still unclear how easily these models can be applied to videos taken from the infant perspective.

In the present paper, we make progress on understanding the relationship  between the infant visual perspective and motoric and linguistic development in three ways. First, we validate a model for the automated detection of faces and hands in the infant view. We use an open-source model of pose detection -- OpenPose [@zhang2016; @cao2017realtime] -- that provides pose, face, and hand keypoints for every person in an image.  We compare the detection accuracy of this method with that of both older and more specialized models of face detection, and demonstrate the usability of this off-the-shelf model for quantifying the faces and hands in the infant view.

Second, we provide an annotated, open dataset for researchers to examine the effects of postural developments and naming behavior during naturalistic parent-child interactions. To do so, we invited caregivers of 8, 12, and 16-month-olds to participate in play sessions where they were provided with pairs of novel and familiar objects (e.g., a ball and a microfiber duster, called a "zem"). We chose this age-range to span the months when infants typically transition from sitting to crawling to standing, and documented the infant egocentric view as well as a third-person view of the play session. We then annotated infants' in-the-moment posture and orientation relative to their caregiver, and obtained full transcripts of the play sessions as well as MacArthur-Bates Communicative Development Inventories for each child.

Third, we apply our automated method to this and one other openly available head-mounted camera dataset, examining the generality of the effects of motor development on the social information in view. In Study 1, we use the cross-sectional design of our dataset to directly examine the relative contributions of age vs. in-the-moment posture on infants' visual access to social information, and use the transcriptions to examine how the availability of social cues changes relative to naming events (e.g., “Yes, you like the [ball!]”). Indeed, despite positing links between the social information in view and language development, no work to date has directly examined how the availability of social information changes around naming events in naturalistic contexts. 
In Study 2, we apply this automated method to @franchak2017see, where one-year-olds wore head-mounted eye-tracking cameras during a play session and their in-the-moment posture was hand-annotated.  Unlike in Study 1, infants and caregivers roamed a large, open playroom and explored different toys placed throughout. We thus analyze this second dataset with a first goal of  validating our automated method on a very different kind of video dataset, attempting to replicate their primary findings originally obtained with a head-mounted eye-tracker, and then further examine whether the proportion of hands in view also varies with infants’ posture. 
Broadly, we predicted that there would be differential access to social information based on children's postural developments: crawling infants would see fewer faces/hands because they would primarily be looking at the ground, while walking toddlers would have access to a richer visual landscape with greater access to the social information in their environment.

# Study 1
## Methods
Caregivers of 8, 12, and 16-month-olds were invited to participate in play sessions where they were provided with pairs of novel and familiar objects (e.g., a ball and a microfiber duster, called a "zem") in a small playroom in a lab (approximately 10' x 10'). Infants wore head-mounted cameras equipped with a fish-eye lens (see Head-mounted camera); a tripod-mounted camera captured a third-person view of the play session. Using these video data, infants' posture and orientation to their caregiver were hand-coded and annotated for the entirety of the play session. All videos were transcribed, and MacArthur CDIs were collected for all children who participated. All materials have been made publicly available on Databrary for whom the parents provided sharing consent (29/36 dyads) via [BLINDED].

@@

sub_summary <- all_subs %>%
  left_join(inc_subs) %>%
  group_by(age_group) %>%
  summarise(n = sum(inc),
            percent_included = mean(inc),
            age = mean(age.at.test, na.rm=TRUE),
            video_length = mean(len.min, na.rm=TRUE),
            female = sum(gender=="female", na.rm=TRUE))

colnames(sub_summary) <- c('Group','N','% incl.','Avg. age', 'Avg video length', 'Num female')

```
Our final sample consisted of 36 infants and children, with 12 participants in three age groups: 8 months (6 F), 12 months (7 F), and 16 months (6 F). Participants were recruited from the surrounding community via state birth records, had no documented disabilities, and were reported to hear at least 80 percent English at home. Demographics and exclusion rates are given in the table below (see Table 1).

```{r, echo=F}
apa_table(sub_summary, caption = "Exclusion rates and summary demographics for the infants included in the study.")
```

@@

We used a head-mounted camera ("headcam") that was constructed from a small camera attached to a soft elastic headband.[^2]  Initial participants wore an MD-80 camera, which was then replaced by a Veho pro camera which had better battery life and a larger view angle. The view angle of the MD-80 camera was $32^{\circ}$ horizontal by $24^{\circ}$ vertical, and we attached a fish-eye lens to the camera to increase the view angle to $64^{\circ}$ horizontal by $46^{\circ}$ vertical. The view angle of the Veho pro camera was wider, $47^{\circ}$ horizontal by $36^{\circ}$ vertical. Videos captured by MD-80/Veho cameras  were 640x480/720x480 pixels, respectively, and both cameras had a frame rate of ~30 frames per second. To ensure that detections across these different cameras were comparable, we excluded detections from the outer edges of the videos taken with the MD-80 cameras based on these view angle differences in our main analyses (i.e. excluding top/bottom 13% of the frames, and left/right 10% of the frames).

[^2]: Detailed instructions for creating this headcam can be found at [BLINDED].

However, the vertical field of view of the cameras were still considerably reduced compared to the infants' field of view, which spans around 100--120$^{\circ}$ in the vertical dimension by 6-7 months of age [@mayer1988;@cummings1988]. As we were primarily interested in the presence of faces in the child's field of view, we chose to orient the camera upwards to capture the entirety of the child's upper visual field where the child is likely to see adult faces, understanding that this decision limited our ability to detect hands (especially those of the child, which are typically found at the bottom of the visual field). We note that these limitations regarding field of view and camera angle affect all studies using this method, not only our own.

@@

## OpenPose detections key
## faceOP, wristOP == faces and wrists in equalized FOV across cameras
## faceOPAll, wristOPAll == faces and wrists of all confidences across all areas of the frames
## "faceOPStrict", "wristOPStrict" == faces and wrists in equalized FOV across cameras with high confidence
## "faceOPStrictAll", "wristOPStrictAll" == faces and wrists across all areas of the frames  with high confidence
```

```{r}
## make long form version for plotting both face detections on same graph
dlong <- d %>%
  mutate(id = paste(subid,frame)) %>%
  gather(key = detectorType, value = detection, faceMT, faceOP, faceOPAll, faceOPStrict, faceOPStrictAll, faceVJ, wristOP, wristOPAll, wristOPStrict, wristOPStrictAll) %>%
  mutate(detectorType=as.factor(detectorType))  %>%
  mutate(detection = replace_na(detection,FALSE)) ## few frames where OP didn't have detections

@@

#### Posture and caregiver orientation annotations
We created custom annotations to describe the child's physical posture (i.e. standing) and the orientation of the caregiver relative to the child (e.g. far away). The child's posture was categorized as being carried, prone (crawling or lying), sitting, or standing. The caregiver's orientation was characterized as being close, far, or behind the child (independent of distance). For the first two annotations (close/far from the child), the caregiver could either be to the front or side of the child. All annotations were made by a trained coder using the OpenSHAPA/Datavyu software [@adolph2012toward]. Times when the child was out of view of the tripod camera were marked as uncodable and were excluded from these annotations; similarily, times when the child was being carried or the caregivers were out of the frame were marked as uncodable for caregiver orientation. On average, posture or orientation was uncodable from 1-2 minutes of data in each child (seconds excluded from analysis for posture, M = `r round(NA_rates$mean_na_posture,0)`s, SD = `r round(NA_rates$sd_na_posture,0)`s; orientation; M = `r round(NA_rates$mean_na_posture,0)`s, SD = `r round(NA_rates$sd_na_posture,0)`s), and these rates did not vary substantially with the age of the child.  To assess the reliability of these annotations, a second coder annotated videos from three different children to calculate Cohen's kappa (posture, $\kappa$ = .82; caregiver orientation, $\kappa$ = .73).

@@

## Face and hand detection
We evaluated three automated detection systems for the ability to measure infants' visual access to faces. The first of these is the most commonly-used and widely available face detection algorithm: Viola-Jones  [@viola2004robust]. We used this algorithm as a benchmark for performance, as while it can achieve impressive accuracy in some situations, it is notoriously bad at dealing with occluded faces [@scheirer2014perceptual]. We next tested the performance of two face detectors that both made use of relatively recently developed Convolutional Neural Networks (CNNs) to extract face information. The first algorithm was specifically optimized for face detection, and the second algorithm was optimized to extract pose information of all the individuals in an image, operationalized as information about the position of 18 different body parts.  For this second algorithm [OpenPose; @cao2017realtime], we used the agent's nose (one of the body keypoints detected) to operationalize the presence of faces, as any half of a face necessarily contains a nose.

@@

### Algorithms
Viola Jones, the first face detection system, made use of a series of Haar feature-based cascade classifiers [@viola2004robust] applied to each individual frame. The second algorithm [based on work by @zhang2016] uses multi-task cascaded convolutional neural networks (MTCNNs) for joint face detection and alignment, built to perform well in real-world environments where varying illuminations and occlusions are present. We used a Tensorflow implementation of this algorithm available at https://github.com/davidsandberg/facenet.

@@

```{r exampledetections, fig.env = "figure", out.width="100%", fig.pos = "H", fig.label="exampledetections", fig.cap = "Example detections made by OpenPose from children in each age group."}
knitr::include_graphics("images/exampe_detections.png")
```

## Results
First, we report the accuracy of the automated detectors, as assessed by comparison to hand-labelled frames from the free-play video dataset described above. We then apply one of these automated detectors (OpenPose) to the entirety of this video dataset, and use these outputs to examine how postural developments influence children's visual access to faces and hands from 8-16 months of age. We further use the detections to examine how access to these social cues changes during naming events (e.g., do you see the [zem]?).

@@

@@

@@
